---
title: "Monty Hall Simulation"
author: "Austin Hart"
date: "Jan 14, 2026"
format: html
knitr:
  opts_chunk: 
    echo: true
    eval: true
    message: false
    collapse: true
    warning: false
    comment: "#>"
---

# My Simulation

I began by loading the required packages.

```{r}
library(tidyverse)
library(knitr)
```

My next steps are to set the stage -- creating three doors -- and to set a score sheet to track results.

```{r}
## set the stage
doors <- c('A', 'B', 'C')

## keep score
results <- tibble(
  trial = 1:10000
)
```

Finally I run the game. I place the prize at random, and the contestant choose a door at random. The host opens a door to reveal a goat. Then the contestants act: Marilyn switches doors while Paul does not. I repeat the game 10,000 times and record the winners in the `results` object created previously.

```{r}
for (i in 1:10000){
  car <- sample(doors, 1) # puts car behind 1 door at random
  choice <- sample(doors, 1)
  reveal <- sample(doors[doors != car & doors != choice], 1)
  switch <- sample(doors[doors != choice & doors != reveal], 1)
  results[i, 'winner'] <- if_else(car == choice, "Paul wins", "Marilyn wins")
}
```

# Results

The table below presents the results of the simulation.

```{r}
outcomes <- 
  results |>
  count(winner) |>
  mutate(percent = n / sum(n) * 100)

kable(outcomes, caption = 'Results of simulation', digits = 1L)
```

In 10,000 simulations, the contestant who switched won a total of `r results |> filter(winner == "Marilyn wins") |> nrow()` times. This is consistent with Marilyn's expectation. You should switch!